\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-06-23 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
updating Section V

\subsection{Synthetic Test System}\label{subsec:NumSimSynthetic}

>>>>

\begin{table}[t]
\centering
\begin{tabular}{| l | l |} 
\hline
Description & Values\\
\hline\hline
&\\
frequency & $f_{0} = 60$ Hz\\
&\\
inertia & $m_{i}\in{\rm{Unif}}\left([2,12]\right)/2\pi f_{0}$\\
& \\
damping coefficient & $\gamma_{i}\in{\rm{Unif}}\left([20,30]\right)/2\pi f_{0}$\\
& \\
diffusion coefficient & $\sigma_{i}\in{\rm{Unif}}\left([1,5]\right)$\\
& \\
\hline
\end{tabular}
\caption{Parameters used for the numerical simulation reported in Sec. \ref{subsec:NumSimSynthetic}.}
\label{table:ParamUncertaintiesSynthetic}
\end{table}

\subsection{Synthetic Test System}\label{subsec:NumSimSynthetic}
We consider a power network with $n=20$ generators.
